draft

### 2025-05-17 draft.tex
Updates from Overleaf

\begin{figure}[htbp]
\centering
\includesvg[width=.9\linewidth]{./figs/jump_r2_examples}
\caption{\label{fig:cp_vs_cpmeasure}We recapitulate the CellProfiler features. \textbf{Left panel.} Representative examples comparing Cellprofiler feature values to $$cp_measure$$, obtained from the same sets of masks and images. \textbf{Right panel.} $$R^2$$ value of a linear fit for each individual feature, comparing $$cp_measure$$ to CellProfiler.}
\end{figure}

>>>>

\begin{figure}[htbp]
\centering
\includesvg[width=.9\linewidth]{./figs/jump_r2_examples}
\caption{\label{fig:cp_vs_cpmeasure}We recapitulate the CellProfiler features. \textbf{Left panel.} Representative examples comparing Cellprofiler feature values to cp_measure, obtained from the same sets of masks and images. \textbf{Right panel.} $R^2$ value of a linear fit for each individual feature, comparing cp_measure to CellProfiler.}
\end{figure}
